Security Properties for Stack Safety

### 2021-05-17 short/main.tex
wibbles

Our threat model is very strong, allowing the attacker (i.e., the callee) to
execute arbitrary code, including attempting to smash
the stack to disrupt the program's control flow.
Our stack safety properties demand that, even in the presence of such
attackers, confidentiality and integrity
still apply to data in suspended stack frames until the callee returns.
The question then arises:
what constitutes a return in this setting? It is not obvious, since
our machine model is a low-level ISA where the same opcode might
sometimes
be used to return from a call and sometimes for other purposes.
Our solution is to associate, with each dynamic call in an execution trace, a
``return target'' that records the address of the instruction following the
call and the stack pointer when the call was made. Thus, so the callee may
execute instructions outside of its normal footprint, perhaps due to
smashing the stack, but
the caller is protected until the PC and SP simultaneously match its return
target.

@@

Our testing supports the stack-safety claim of Roessler and Dehon's {\em Depth
  Isolation} micro-policy, in
which memory cells within each stack frame are tagged with the depth of
the function activation that owns the frame and access to those locations is
then permitted only when that activation is currently executing.
On the other hand, we find that their \emph{Lazy Tagging and Clearing} policy
violates the temporal aspect of confidentiality in
corner cases where data can leak across repeated calls to the same callee,
and also violates integrity if the leak happens to use the caller's frame. We
propose a variant of {\em Lazy Tagging and Clearing} that
  we believe will enforce observational
integrity and confidentiality, albeit at some performance cost. (An obvious next step
is to expand testing to these properties and validate the variant, but
efficiently
testing observational properties is more challenging because a property
violation can be arbitrarily far removed from the initial ``risky'' read or
write.)

>>>>

Our threat model is very strong, allowing the attacker (i.e., the callee) to
execute arbitrary code, including attempting to smash
the stack to disrupt the program's control flow.
Our stack safety properties demand that, even in the presence of such
attackers, confidentiality and integrity
still apply to data in suspended stack frames until the callee returns.
The question then arises:
what constitutes a return in this setting? It is not obvious, since
our machine model is a low-level ISA where the same opcode might
sometimes
be used to return from a call and sometimes for other purposes.
Our solution is to associate, with each dynamic call in an execution trace, a
``return target'' that records the address of the instruction following the
call and the stack pointer when the call was made. Thus, the callee may
execute instructions outside of its normal footprint, perhaps due to
smashing the stack, but
the caller is protected until the PC and SP simultaneously match its return
target.

@@

Our testing supports the stack-safety claim of Roessler and Dehon's {\em Depth
  Isolation} micro-policy, in
which memory cells within each stack frame are tagged with the depth of
the function activation that owns the frame and access to those locations is
then permitted only when an activation at that depth is currently executing.
On the other hand, we find that their \emph{Lazy Tagging and Clearing} policy
violates the temporal aspect of confidentiality in
corner cases where data can leak across repeated calls to the same callee,
and also violates integrity if the leak happens to use the caller's frame. We
propose a variant of {\em Lazy Tagging and Clearing} that
  we believe will enforce observational
integrity and confidentiality, albeit at some performance cost. (An obvious next step
is to expand testing to these properties and validate the variant, but
efficiently
testing observational properties is more challenging because a property
violation can be arbitrarily far removed from the initial ``risky'' read or
write.)
